### 2017-09-26 Sections/optical_encoding_of_quantum_information.tex
easy sampling LO problems

In phase-space, the most common representations of optical states are in terms of quasi-probability functions:
\begin{itemize}\index{$P$-function}\index{$Q$-function}\index{Wigner function}
\item $P$-function: represents a state as a quasi-mixture of coherent states. When the $P$-function is strictly non-negative, it can be interpreted as a perfect classical mixture of coherent states. However, with any negativity this classical interpretation breaks down, hence `quasi'-probability. In general, the $P$-function representation for a state is not unique.
\begin{align}
\hat\rho = \int\!\!\!\int P(\alpha) \ket{\alpha}\bra{\alpha} d^2\alpha.
\end{align}
\item $Q$-function: represents a state in terms of its overlap with the complete set of all coherent states, which form an over-complete basis.
\begin{align}
Q(\alpha) = \frac{1}{\pi} \bra{\alpha}\hat\rho\ket{\alpha}.
\end{align}
\item Wigner function: also has a quasi-probability interpretation, and negativity is qualitatively associated with `quantumness'. The Wigner function of a state is unique, and isomorphic to the density operator, making it perhaps the most useful phase-space representation for quantum states of light.
\begin{align}
W(x,p) = \int e^{ips/\hbar} \left\langle{x-\frac{s}{2}}\right| \hat\rho \left|{x+\frac{s}{2}}\right\rangle ds.
\end{align}
\end{itemize}
These representations, whilst entirely equivalent to a photon-number basis representation, are far easier to work with for many types of states. Most notably, Gaussian states are conveniently represented and manipulated using phase-space representations.

>>>>

In phase-space, the most common representations of optical states are in terms of quasi-probability functions\index{Quasi-probability functions}\footnote{The term `quasi-probablity' arises because in some regimes (for example, strictly non-negative $P$-functions), the function has a true probabilistic interpretation. However this interpretation breaks down for any negativity in the $P(\alpha)$, since negative probabilities have no meaningful classical interpretation.}:
\begin{itemize}\index{$P$-function}\index{$Q$-function}\index{Wigner function}
\item $P$-function: represents a state as a quasi-mixture of coherent states. When the $P$-function is strictly non-negative, it can be interpreted as a perfect classical mixture of coherent states. However, with any negativity this classical interpretation breaks down, hence `quasi'-probability. In general, the $P$-function representation for a state is not unique.
\begin{align}
\hat\rho = \int\!\!\!\int P(\alpha) \ket{\alpha}\bra{\alpha} d^2\alpha.
\end{align}
\item $Q$-function: represents a state in terms of its overlap with the complete set of all coherent states, which form an over-complete basis.
\begin{align}
Q(\alpha) = \frac{1}{\pi} \bra{\alpha}\hat\rho\ket{\alpha}.
\end{align}
\item Wigner function: also has a quasi-probability interpretation, and negativity is qualitatively associated with `quantumness'. The Wigner function of a state is unique, and isomorphic to the density operator, making it perhaps the most useful phase-space representation for quantum states of light.
\begin{align}
W(x,p) = \int e^{ips/\hbar} \left\langle{x-\frac{s}{2}}\right| \hat\rho \left|{x+\frac{s}{2}}\right\rangle ds.
\end{align}
\end{itemize}
These representations, whilst entirely equivalent to a photon-number basis representation, are far easier to work with for many types of states. Most notably, Gaussian states are conveniently represented and manipulated using phase-space representations.

### 2017-09-26 Sections/physical_architectures_for_quantum_computing.tex
easy sampling LO problems

@@

@@

On the other hand, some classes of optical states are known to be efficiently classically simulable under linear optics evolution and photo-detection. This includes coherent states, thermal states, or any state with strictly positive $P$-function\footnote{A strictly positive $P$-function implies that the state can be considered a purely classical mixture of coherent states (each of which are classically efficient to simulate), according to some probability distribution.} (Sec.~\ref{sec:exotic}) \cite{bib:SalehQOCCC15, bib:SalehEffSim16}. Furthermore, Gaussian states evolved via linear optics and measured using Gaussian measurements have been shown to be computationally easy to simulate \cite{bib:Bartlett02, bib:Bartlett02b}.

@@

\paragraph{Easy problems}\index{Easy linear optics sampling problems}

@@

A linear optics network acting on a tensor product of coherent state inputs implements simple matrix multiplication on the vector of coherent amplitudes. Specifically, Eq.~(\ref{eq:LO_unitary_map}) implies that for the input multi-mode coherent state,
\begin{align}
\ket{\psi}_\text{in} = \ket{\vec\alpha} = \ket{\alpha_1,\dots,\alpha_m},
\end{align}
where $\alpha_i$ is the coherent amplitude of the $i$th mode, the linear map now takes the form,
\begin{align}
\beta_i = \sum_{j=1}^m U_{i,j} \alpha_j,
\end{align}
where the output state is the separable multi-mode coherent state,
\begin{align}
\ket{\psi}_\text{out} = \ket{\vec\beta} = \ket{\beta_1,\dots,\beta_m}.
\end{align}
Equivalently, this could simply be expressed as the matrix equation,
\begin{align}
\vec{\beta} = U\cdot\vec{\alpha}.
\end{align}

Of course this is not strictly a \textit{quantum} computation, since:
\begin{itemize}
\item It can be efficiently classically computed using $O(m^2)$ operations\footnote{Using the na\"ive element-wise approach, which can be further improved upon using more sophisticated contemporary algorithms.}, thus residing in \textbf{P}\index{\textbf{P} \& \textbf{BPP}}.
\item Coherent states are considered classical states (i.e laser light) with strictly positive Wigner functions\index{Wigner function}.
\item There is no entanglement between modes.
\item The algorithm offers no quantum speedup.
\end{itemize}

@@

%
% Hybrid Architectures
%

\subsection{Hybrid architectures} \label{sec:hybrid} \index{Hybrid architectures}

@@

The natural example is matter qubits which couple to single-photon states, whereupon which-path erasure between coupled optical modes teleports entanglement onto the physical matter qubits.\index{Which-path erasure} Similarly, measurement of the matter qubits may be performed by stimulating the emission of photons from them. This idea has been applied to $\lambda$-configuration atomic qubits \cite{bib:BarrettKok05}, shown in Fig.~\ref{fig:barrett_kok}, and atomic ensemble qubits \cite{bib:RohdeAtEns10} (Sec.~\ref{sec:atomic_ens}). The protocol is described in Alg.~\ref{alg:which_path}.

Optically-mediated atomic ensemble quantum computing architectures are particularly attractive, as discussed in Sec.~\ref{sec:atomic_ens}\index{Atomic ensembles}.

A novel `double heralding' technique, introduced in \cite{bib:BarrettKok05}, allows loss to be overcome during which-path erasure \comment{Check this, is this what the double heralding does?}. Similarly, quantum states of light can be coupled to two-level quantum systems using Hamiltonians of the form shown in Eq.~(\ref{eq:two_level_hamil}). The preparation of long-distance entanglement between atomic systems has been demonstrated \cite{bib:Matsukevich05, bib:Matsukevich05b}

@@

Importantly, the beamsplitter mediating the which-path erasure EO is based upon HOM interference, and therefore does not require interferometric stability, making the outsourcing process relatively robust.

@@

>>>>

A linear optics network acting on a tensor product of coherent state inputs implements simple matrix multiplication\index{Matrix multiplication} on the vector of coherent amplitudes. Specifically, Eq.~(\ref{eq:LO_unitary_map}) implies that for the input multi-mode coherent state,
\begin{align}
\ket{\psi}_\text{in} = \ket{\vec\alpha} = \ket{\alpha_1,\dots,\alpha_m},
\end{align}
where $\alpha_i$ is the coherent amplitude of the $i$th mode, the linear map now takes the form,
\begin{align}
\beta_i = \sum_{j=1}^m U_{i,j} \alpha_j,
\end{align}
where the output state is the separable multi-mode coherent state,
\begin{align}
\ket{\psi}_\text{out} = \ket{\vec\beta} = \ket{\beta_1,\dots,\beta_m}.
\end{align}
Equivalently, this could simply be expressed as the matrix equation,
\begin{align}\label{eq:coherent_state_LO_map}
\vec{\beta} = U\cdot\vec{\alpha}.
\end{align}

Of course this is not strictly a \textit{quantum} computation, since:
\begin{itemize}
\item It can be efficiently classically computed using $O(m^2)$ operations\footnote{Using the na\"ive element-wise approach, which can be further improved upon using more sophisticated contemporary algorithms.}, thus residing in \textbf{P}\index{\textbf{P} \& \textbf{BPP}}.
\item Coherent states are considered classical states (i.e approximated by laser light\index{Laser light}) with strictly positive Wigner and $P$-functions\index{Wigner function}\index{$P$-function}.
\item There is no entanglement between modes.
\item The algorithm offers no quantum speedup.
\end{itemize}

@@

Beyond photonic {\sc BosonSampling}, much investigation has explored the computational hardness of other types of linear optics sampling problems, using states beyond just single photons.

@@

\paragraph{Easy problems}\label{sec:easy_LO_probs}\index{Easy linear optics sampling problems}

On the other hand, some classes of optical states are known to be efficiently classically simulable under linear optics evolution and photo-detection. This includes coherent states, thermal states, or any state with strictly positive $P$-function\footnote{A strictly positive $P$-function implies that the state can be considered a purely classical mixture of coherent states (each of which are classically efficient to simulate), according to some classical probability distribution.} (Sec.~\ref{sec:exotic}) \cite{bib:SalehQOCCC15, bib:SalehEffSim16}. Furthermore, Gaussian states evolved via linear optics and measured using Gaussian measurements have been shown to be computationally easy to simulate \cite{bib:Bartlett02, bib:Bartlett02b}.

While such negative results might be somewhat depressing, it is extremely insightful to understand these regimes, in the interest of avoiding investing excrutiating effort into trying to instead fruitlessly prove that they are hard.

@@

The simplest example of an easy such problem is coherent state linear optics\index{Coherent state linear optics}, as discussed in Sec.~\ref{sec:coherent_state_QC}. Taking this notion further, recall from Sec.~\ref{sec:exotic} that one of the phase-space\index{Phase-space} representations for generic optical states is the $P$-function\index{$P$-function}, which represents a density operator as a sum over coherent state,
\begin{align}
\hat\rho = \int\!\!\!\int P(\alpha) \ket{\alpha}\bra{\alpha} d^2\alpha.
\end{align}
Here $P(\alpha)$ is a quasi-probability function\index{Quasi-probability function}. Importantly, iff the $P$-function is strictly non-negative, \mbox{$P(\alpha)\geq 0 \,\,\forall \,\alpha$}, the optical state may be trivially interpreted as a purely classical mixture of coherent states ($P(\alpha)$ would be a delta function for pure coherent states). If, on the other hand, the $P$-function exhibits negativity for any $\alpha$, this interpretation breaks down and is indicative of the state exhibiting non-classical\index{Non-classical states} behaviour.

Alg.~\ref{alg:positive_P_sim} describes an efficient classical algorithm for simulating the output photo-statistics of a linear optics sampler fed with strictly non-negative $P$-function input states.

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function SimulatePositiveP($\vec{P}$):
\begin{enumerate}
	\item for(m$\in$modes) \{
	\setlength{\itemindent}{0.2in}
	\item Randomly choose a sample $\alpha_m$ from probability density function $P_m(\alpha)$\index{Probablity density function}.
	\setlength{\itemindent}{0in}
		\item \}
		\item Evolve the set of input coherent states through the linear optics network,
		\begin{align}
		\vec\beta = U\cdot\vec\alpha.
		\end{align}
	\item for(m$\in$modes) \{
	\setlength{\itemindent}{0.2in}
	\item The probability of measuring $n$ photons in the $m$th mode is given by the distribution,
	\begin{align}
	D_{m,n} = e^{-\frac{|\beta_m|^2}{2}} \frac{{\beta_m}^n}{\sqrt{n!}}.
	\end{align}
	\item Choose $n$ from this distribution.
	\setlength{\itemindent}{0in}
	\item \}
	\item return($\vec{n}$).
    \item $\Box$
\end{enumerate}}}}
\caption{Efficient classical algorithm for simulating any linear optics sampling problem whose input states have strictly non-negative $P$-functions, with output measured via photon-counting. $\vec{P}$ is the vector of $P$-functions for all modes.} \label{alg:positive_P_sim}
\end{table}

@@

@@

%
% Hybrid Light-Matter Architectures
%

\subsection{Hybrid light-matter architectures} \label{sec:hybrid} \index{Hybrid light-matter architectures}

@@

The natural example is matter qubits which couple to single-photon states, whereupon which-path erasure between coupled optical modes teleports entanglement onto the physical matter qubits\index{Entanglement teleportation}.\index{Which-path erasure} Similarly, measurement of the matter qubits may be performed by stimulating the emission\index{Stimulated emission} of photons from them. This idea has been applied to $\lambda$-configuration atomic qubits\index{Atomic qubits}\index{$\lambda$-configuration systems} \cite{bib:BarrettKok05}, shown in Fig.~\ref{fig:barrett_kok}, and atomic ensemble qubits \cite{bib:RohdeAtEns10} (Sec.~\ref{sec:atomic_ens}). The protocol is described in Alg.~\ref{alg:which_path}.

In principle, this technique could be applied to any physical system comprising natural or engineered $\lambda$-configured energy levels, which couple to accessible optical modes. This light-matter coupling\index{Light-matter coupling} may require carefully constructed optical cavities\index{Optical cavities}, as is the case for single atoms. Alternately, atomic ensemble qubits inherently undergo collective enhancement\index{Collective enhancement} in their light-matter coupling, mitigating the need for optical cavities.

Optically-mediated atomic ensemble architectures are particularly attractive, as discussed in Sec.~\ref{sec:atomic_ens}\index{Atomic ensembles}, owing to their long coherence lifetimes\index{Coherence lifetime}, room temperature operation\index{Room temperature operation}, strong light-matter coupling, and robustness against qubit loss\index{Qubit loss}.

A novel `double heralding'\index{Double heralding} technique, introduced in \cite{bib:BarrettKok05}, allows photon loss\index{Photon loss} to be overcome during which-path erasure \comment{Check this, is this what the double heralding does?}. Similarly, quantum states of light can be coupled to two-level quantum systems using Hamiltonians of the form shown in Eq.~(\ref{eq:two_level_hamil}). The preparation of long-distance entanglement between atomic systems has been demonstrated \cite{bib:Matsukevich05, bib:Matsukevich05b}

@@

Importantly, the beamsplitter mediating the which-path erasure EO is based upon HOM interference, and therefore does not require interferometric stability, making the outsourcing process relatively robust and suitable for long-range operation.

@@

%
% Ion Traps
%

\subsection{Ion traps}\index{Ion traps}

\comment{To do. Talk about optical interfacing.}

%
% Superconducting Rings
%

\subsection{Superconducting rings}\index{Superconducting rings}

\comment{To do. Talk about optical interfacing.}

%
% Adiabatic Quantum Computing & Quantum Annealing
%

\subsection{Adiabatic quantum computing \& quantum annealing}\index{Adiabatic quantum computing}\index{Quantum annealing}

\comment{To do. Talk about optical interfacing.}
